Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-10-27 Article/main.tex
Updated Article

\subsection{Collection of Case Studies and Determine Similarities}
As case studies were accumulated, only those found that discussed - either directly in great detail or indirectly during the game's description -the design principles followed were selected to be used. Notably, many of those chosen had a focus on some form of digital and cyber security including specific mentions to phishing, social engineering and passwords\cite{Sheng2007, Dincelli2020, snyman2021wolf}. 
\\\\
The following step after finding these case studies was to identify their design principles and determine the major ones that most, if not all, made use of as well as how successful the game was found to be - which is determined in the individual publication either by trails of being judged by experts.

@@

\section{Findings}
\subsection{Helpful Instructional Theories}
\subsection{Case Studies and the Similarities in Design Principles}

>>>>

\subsection{Collection of Case Studies and Determine Similarities}
As case studies were accumulated, only those found that discussed - either directly in great detail or indirectly during the game's description -the design principles followed were selected to be used. Notably, many of those chosen had a focus on some form of digital and cyber security including specific mentions to phishing and social engineering\cite{Sheng2007, Dincelli2020}. 
\\\\
The following step after finding these case studies was to identify their design principles and determine the major ones that most, if not all, made use of as well as how successful the game was found to be - which is determined in the individual publication either by trails of being judged by experts.

@@

\section{Findings}
As described in the methodology, a large aspect of the findings comes from the literature review conducted. However, the literature review only provided segmented information that must still be distilled. This includes making note of what instructional theory is most pertinent to this study and breaking down the case studies. It also includes a short discussion on the initial reconsiderations from Kapp\cite{Kapp2012a} regarding the knowledge domains.

\subsection{Helpful Instructional Theories}
\subsection{Case Studies and the Similarities in Design Principles}

\begin{table}[htbp]
\caption{Design Principles Defined by Case Study}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline

\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
\hline
Story-based& Story-based & Clear and Simple Goals  \\
Reflection& Reflection& Quality of Feedback and Rewards  \\
-& Conceptual-Procedural & Structure of the Challenge  \\
-& -& Motion-based Interaction  \\
-& -& Simplicity  \\
\hline

\end{tabular}
\label{tab1}
\end{center}
\end{table}

\subsection{Initial Knowledge Domain Recommendations}
